R Notebook

### 2018-11-19 ICS_CD4.Rmd
cleaning functions - subtract unstim

---
title: "R Notebook"
output:
  html_document: default
  html_notebook: default
---
library(dplyr)
library(reshape2)
Boolean<-select(Cytokine, Donor, TB, SM, Stim, G_4_13_T, G_4_x_T, G_x_13_T, G_4_13_x, x_4_13_T, G_4_x_x, G_x_13_x,
                x_4_x_T, x_x_13_T, G_x_x_T , G_x_x_x, x_x_x_T,  x_4_13_x, x_4_x_x, x_x_13_x)

@@

    scale_color_manual(labels = c("SM(-)", "SM(+)"), values = Palette) +
    scale_x_discrete(breaks=c("X","SM"),
                     labels=c("SM(-)", "SM(+)"))+
    theme_bw()+
    theme(axis.text.x = element_text(angle=65, vjust=0.6)) + 
    facet_wrap(~TB,nrow = 1, scale="free_x")+
    labs(title="Cytokine Frequencies", 
         subtitle="",
         caption="",
         x="TB and Helminth Status",
         y="Frequency of Cytokine+ CD4+ T cells")

>>>>

---
title: "R Notebook"
output:
  html_document: default
  html_notebook: default
---

```{r}
library(dplyr)
library(reshape2)
Boolean<-select(Cytokine, Donor, TB, SM, Stim, G_4_13_T, G_4_x_T, G_x_13_T, G_4_13_x, x_4_13_T, G_4_x_x, G_x_13_x,
                x_4_x_T, x_x_13_T, G_x_x_T , G_x_x_x, x_x_x_T,  x_4_13_x, x_4_x_x, x_x_13_x)

@@

    scale_color_manual(labels = c("SM(-)", "SM(+)"), values = Palette) +
    scale_x_discrete(breaks=c("X","SM"),
                     labels=c("SM(-)", "SM(+)"))+
    theme_bw()+
    theme(axis.text.x = element_text(angle=65, vjust=0.6)) + 
    facet_wrap(~TB,nrow = 1, scale="free_x")+
    labs(title="Cytokine Frequencies", 
         subtitle="",
         caption="",
         x="TB and Helminth Status",
         y="Frequency of Cytokine+ CD4+ T cells")
```
